% this file is called up by thesis.tex
% content in this file will be fed into the main document

%: ----------------------- name of chapter  -------------------------
\chapter{Partial Tree} % top level followed by section, subsection


%: ----------------------- paths to graphics ------------------------

% change according to folder and file names
\ifpdf
    \graphicspath{{X/figures/PNG/}{X/figures/PDF/}{X/figures/}}
\else
    \graphicspath{{X/figures/EPS/}{X/figures/}}
\fi

%: ----------------------- contents from here ------------------------







% ---------------------------------------------------------------------------
%: ----------------------- end of thesis sub-document ------------------------
% ---------------------------------------------------------------------------

\documentclass[PRO,english]{ipsj}
\usepackage{PROpresentation}
\PROheadtitle{2015-2-(10): Manuscript for presentation at IPSJ-SIGPRO, Aug 6, 2015.}

% %\documentclass[JIP,draft]{ipsj}
% \documentclass[JIP]{ipsj}

\usepackage[]{graphicx}
\usepackage{latexsym}

\usepackage{color}
\def\modify#1#2#3{%
  {\underline{\sf{#1}}:} {\color{blue}{#2}} {\color{green}{\mbox{$\Rightarrow$}}} {\color{red}{#3}}}

\setlength{\doublerulesep}{.4pt}
% This is the macro for writing partial tree like pt1.
\def\PT#1{\hbox{\textrm{pt}$_{#1}$}}
% I prepared macros for representing nodes like \Nc{A}{0}, \Nl{A}{0}, \Nr{A}{0}, \Np{A}{0}.
\def\Nc#1#2{\hbox{\texttt{#1$_{#2}$}}}
\def\Nl#1#2{\hbox{+\texttt{#1$_{#2}$}}}
\def\Nr#1#2{\hbox{\texttt{#1$_{#2}$}+}}
\def\Np#1#2{\hbox{+\texttt{#1$_{#2}$}+}}
% This is the macro for writing predicate link.
\def\pred#1#2{#1\to\{#2\}}
%\def\INDEXSET#1{\mathit{#1}_{[0,P)}}
\def\INDEXSET#1{\mathit{#1}_{[P]}}
\def\INDEXSETL#1{\mathit{#1}_{[p]}}

\usepackage[varg]{txfonts}%%!!
\makeatletter%
\input{ot1txtt.fd}
\makeatother%

\newtheorem{property}{Property}

\begin{document}

\title{A Partial-Tree-Based Approach\\ for XPath Query on Large XML Trees}

\affiliate{KUT}{School of Information, Kochi University of Technology,
Kami, Kochi 782--8502, Japan}
\affiliate{AUST}{Department of Computer Science and Engineering, Anhui University of Science and Technology,
Huainan, Anhui, China}

\author{Wei Hao}{KUT,AUST}[188004h@gs.kochi-tech.ac.jp]
\author{Kiminori Matsuzaki}{KUT}[matsuzaki.kiminori@kochi-tech.ac.jp]

\begin{abstract}
XML is a popular data definition language and 
is widely used for representation of arbitrary data structures. 
For queries on XML documents, XPath has commonly been 
 used in many applications. The complexity of 
applying queries increases as the number of nodes in an 
XML document increases. Querying very large XML 
documents becomes really difficult when there is not enough  
computer memory to store and manipulate 
the whole tree data. The objective of this study is to 
develop an algorithm for querying very large XML trees in a
distributed-memory environment. We split a large 
XML document into small chunks and parse the chunks to 
create special trees called partial trees. Then the query is 
executed in parallel on the partial trees. The results from 
the partial trees are concatenated to form the final query 
results for output. The algorithms were tested on a 16-node 
PC cluster, and the experiment results showed a speedup 
of a factor of 6 on 16 nodes. 
\end{abstract}

\begin{keyword}
XML, XPath, XML Query, Parallel Programming, Partial Tree
\end{keyword}

\maketitle

\input{introduction}

\input{xpath}

\input{partialtree}

\input{construction}

\input{query}

\input{evaluation}

\input{relatedwork}

\input{conclusion}

\input{bib}

\begin{biography}

\profile{Wei Hao}{is a Ph.D. student in Kochi University of Technology in Japan and is a Lecture in Anhui University of Science and Technology in China. 
	He received his B.E. and M.S. from Anhui University of Science and Technology in 2004 and 2007, respectively, and began doctoral study since 2014. 
	His current research interest is in parallel programming and XML data processing. }
%
\profile{Kiminori Matsuzaki}{is an Associate Professor of Kochi
  University of Technology in Japan.  He received his B.E., M.S. and
  Ph.D. from The University of Tokyo in 2001, 2003 and 2007,
  respectively.  He was an Assistant Professor (2005--2009) in The
  University of Tokyo, before joining Kochi University of Technology
  as an Associate Professor in 2009.  His research interest is in
  parallel programming and algorithm derivation. He is a member of
  ACM, JSSST, IEEE\@.}
%
\end{biography}

\end{document}


